Type-Safe Modular Parsing

### 2017-06-05 SLE_17/paper.tex
Author info and a footnote in case study

%% For double-blind review submission
\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=false}
\settopmatter{printacmref=false}
%% For single-blind review submission
%\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[sigplan,10pt]{acmart}\settopmatter{}

@@

@@

%% Author with single affiliation.
\author{First1 Last1}
\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position1}
  \department{Department1}              %% \department is recommended
  \institution{Institution1}            %% \institution is required
  \streetaddress{Street1 Address1}
  \city{City1}
  \state{State1}
  \postcode{Post-Code1}
  \country{Country1}
}
\email{first1.last1@inst1.edu}          %% \email is recommended

%% Author with two affiliations and emails.
\author{First2 Last2}
\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}
}
\email{first2.last2@inst2b.org}         %% \email is recommended

>>>>

%% For double-blind review submission
%% \documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=false}
%% For single-blind review submission
\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[sigplan,10pt]{acmart}\settopmatter{}

@@

\settopmatter{printacmref=false}

@@

%% Author with single affiliation.
\author{Haoyuan Zhang}
\email{hyzhang@cs.hku.hk}          %% \email is recommended

\affiliation{
  \institution{The University of Hong Kong}            %% \institution is required
}

\author{Huang Li}
\email{hli@cs.hku.hk}          %% \email is recommended
%% \authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  %% \position{Position1}
  %% \department{Department1}              %% \department is recommended
  \institution{The University of Hong Kong}            %% \institution is required
  %% \streetaddress{Street1 Address1}
  %% \city{City1}
  %% \state{State1}
  %% \postcode{Post-Code1}
  %% \country{Country1}
}

\author{Bruno C. d. S. Oliveira}
\email{bruno@cs.hku.hk}          %% \email is recommended

\affiliation{
  \institution{The University of Hong Kong}            %% \institution is required
}
%% Author with two affiliations and emails.
%% \author{First2 Last2}
%% \authornote{with author2 note}          %% \authornote is optional;
%%                                         %% can be repeated if necessary
%% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%% \affiliation{
%%   \position{Position2a}
%%   \department{Department2a}             %% \department is recommended
%%   \institution{Institution2a}           %% \institution is required
%%   \streetaddress{Street2a Address2a}
%%   \city{City2a}
%%   \state{State2a}
%%   \postcode{Post-Code2a}
%%   \country{Country2a}
%% }
%% \email{first2.last2@inst2a.com}         %% \email is recommended
%% \affiliation{
%%   \position{Position2b}
%%   \department{Department2b}             %% \department is recommended
%%   \institution{Institution2b}           %% \institution is required
%%   \streetaddress{Street3b Address2b}
%%   \city{City2b}
%%   \state{State2b}
%%   \postcode{Post-Code2b}
%%   \country{Country2b}
%% }
%% \email{first2.last2@inst2b.org}         %% \email is recommended
